Understanding Factors Influencing Waterfowl Counts on Toronto Beaches

### 2024-12-03 paper/paper.qmd
Change format of files.

library(tidyverse)
library(modelsummary)
library(here)
library(broom.mixed)
library(rstanarm)
```

@@

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

>>>>

library(tidyverse)
library(modelsummary)
library(here)
library(broom.mixed)
library(rstanarm)
library(arrow)
```

@@

analysis_data <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))
